Cover letter for the original IJRR submission

### 2017-10-04 reviews_tro/reviewer_response.tex

\quot{in my opinion a T-RO regular paper should be more self-containing. In several points the authors heavily rely on previous publications, e.g. when presenting the RRT-based planner (Section IV-C). This part should be expanded, describing in more detail what exactly has been changed with respect to the reference paper. }
\as{Thanks for the comment. As it is also suggested by reviewer 1 and the AE, we modified the paper to make it self contained. The references to previous work now solely indicate
that a certain method is not a contribution of the present paper. \\ 
In the particular case of Section IV-C, in fact the code of our implementation of the Bi-RRT with respect to the original one is exactly the same, with a single difference: when
traditionally a collision detection predicate is called to validate a configuration, we replace this predicate with a call to the reachability condition. We modified the text to explain this more clearly. As the Bi-RRT is a famous standard algorithm in the literature, we do not think it is necessary to include it in this paper, but we will gladly do so if required. }
\qt{$C_{Reach}^0$ can be sampled efficiently thanks to Eq.~5, and can thus be used with any standard motion planner.
Our current implementation uses the Bi-RRT planner [25] provided by the HPP software [26].
Our implementation is exactly the same as the pseudo-code of the original planner (which does not detail the configuration validation method). With respect to a ``classic'' implementation, the only difference is that instead of validating a configuration using collision detection, we validate it with the \textit{reachability condition}.} \done

\quot{I am a bit skeptical about the readability of the figures. Some of them seem to be too small (e.g. Fig. 3, Fig. 4), some are of quite poor quality (why the robot silhouettes in Fig. 4 are blurred ?), and the purpose and meaning of Fig. 6 is rather unclear. \\ In general, the simulation results presented qualitatively in the paper are a bit hard to interpret without the accompanying video, particularly if someone looks at a b/w print of the paper (as it may be looking in T-RO).}
\as{Thanks for the comment, with which we agree in general.  \\We increased the size of Fig. 3 and 4. The robot silhouettes in Fig. 4 are blurred when they describe a previous state of the robots. We added this precision in the text. \\Regarding the quality of our Figures,  our simulation Figures are taken from high resolution rendering in blender. The other Figures are drawn from manually designed powerpoint vectorial graphics (converted to png). We assume that the issue encountered comes from the compression of the pdf file to fit the size constraints of the 
submission site. We tried to improve this compression, but if the paper is accepted, we believe that the uncompressed pdf obtained from the source of the paper will result in good quality pictures. If the reviewers think the paper would be better without these figures, we are willing to remove them. However, we believe that they would make the paper more dependent on the video, so we would prefer to leave them. \\ As proposed also by reviewer 1, we removed references to previous results obtained in [20], so the Fig. 6 has been removed.}\ndone

%~ \quot{In general, the simulation results presented qualitatively in the paper are a bit hard to interpret without the accompanying video, particularly if someone looks at a b/w print of the paper (as it may be looking in T-RO).}
%~ \as{ThAll of our simulation figures are taken from high resolution rendering in blender, so we wouldn't know how to improve their quality. If the reviewers think the paper would be better without these figures, we are willing to remove them. However, we believe that they would make the paper more dependent on the video, so we would prefer to leave them.}
%\as{\textbf{\textcolor{red}{TODO This is true, although I think he has a crappy printer because I don't think it's that bad. I don't know what to do about it though. I can't simply remove the Figures, because he tends to say he would like the paper to be more independent from the video...}}}\ndone

### 2017-10-04 body/contact.tex
rescaled figures 3 and 4

% !TEX root =  ../main.tex
\section{From a guide path to a discrete sequence of contact configurations ($\mathcal{P}_2$)}
\label{sec:contact}
In the second phase, we compute a discrete sequence of static equilibrium configurations $\mathbf{Q}^{\overline{0}}$ given a root path
$\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Reach}^0$}. This contact planner uses a contact generator, used to generate static equilibrium configurations. We first describe the contact planning algorithm, before describing
the contact generator.
%~ Our planner computes guide paths in $C_{Reach}^0$ , an approximation of \gls{$C_{Equil}^0$}.
%~ As an input of this stage, we however assume an \gls{equilibrium feasible} root guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Equil}^0$}.
%~ If this is not the case, our planner will fail rapidly, thus allowing replanning, as discussed in Section~\ref{sec:perf}.
%~ We now consider the second problem of computing a discrete sequence of equilibrium configurations $\mathbf{Q}^{\overline{0}}$ along $\mathbf{q}^0(t)$.

@@

\begin{figure}[t]
\centering
  \begin{overpic}[width=0.9\linewidth]{figures/break_contact}
		\put (0,4) {1} 
		\put (25,4) {2} 
		\put (50,4) {3} 
		\put (76,4) {4} 
		%~ \put (68,58) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
\caption{Contacts are maintained if joint limits and collisions constraints are respected (2). They are broken otherwise(3,4). The green line represents the root path.}
		   \label{fig:break_contact}
\end{figure}

>>>>

% !TEX root =  ../main.tex
\begin{figure*}[!hbtp]
\centering
  \begin{overpic}[width=0.6\linewidth]{figures/break_contact}
		\put (0,4) {1} 
		\put (25,4) {2} 
		\put (50,4) {3} 
		\put (76,4) {4} 
		%~ \put (68,58) {3.a)} 
		%~ \put (5,27) {3.b)} 
		%~ \put (37,27) {4.a)} 
		%~ \put (68,27) {4.b)} 
	\end{overpic}
\caption{Contacts are maintained if joint limits and collisions constraints are respected (2). They are broken otherwise(3,4). The green line represents the root path. The blurred character
represents the previous contact configuration.}
		   \label{fig:break_contact}
\end{figure*}

\section{From a guide path to a discrete sequence of contact configurations ($\mathcal{P}_2$)}
\label{sec:contact}

In the second phase, we compute a discrete sequence of static equilibrium configurations $\mathbf{Q}^{\overline{0}}$ given a root path
$\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Reach}^0$}. This contact planner uses a contact generator, used to generate static equilibrium configurations. We first describe the contact planning algorithm, before describing
the contact generator.
%~ Our planner computes guide paths in $C_{Reach}^0$ , an approximation of \gls{$C_{Equil}^0$}.
%~ As an input of this stage, we however assume an \gls{equilibrium feasible} root guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow$ \gls{$C_{Equil}^0$}.
%~ If this is not the case, our planner will fail rapidly, thus allowing replanning, as discussed in Section~\ref{sec:perf}.
%~ We now consider the second problem of computing a discrete sequence of equilibrium configurations $\mathbf{Q}^{\overline{0}}$ along $\mathbf{q}^0(t)$.

@@

### 2017-10-04 body/overview.tex
octree environment
rescaled figures 3 and 4

Figure~\ref{fig:framework} illustrates our work flow.
\Pa and \Pb are addressed sequentially: From a given problem (a) we first plan a root guide path (b), before
extending it into a sequence of static equilibrium configurations (c). In the case where step (c) fails,
our framework invalidates the computed guide path, and restarts the planning from (b).

@@

@@

\medskip
\textbf{The environment} $O$ is defined as the union of the obstacles $O_i$ that it contains.

@@

%~ Finally, we define $dist(\mathbf{x}, O)$ as the minimal distance between a point $\mathbf{x}$ and the closest surface of the environment.
\begin{figure}
  \centering
  \includegraphics[width=0.95\linewidth]{figures/HyQ_roms}
  \caption{
           Reachable workspace and torso bounding box of HyQ. Each green shape represent a reachable workspace $W^k$ of a limb. The red shape is $W^0$.}
		   \label{fig:HyQ_roms}
\end{figure}

>>>>

\begin{figure*}[!htbp]
  \centering
  \includegraphics[width=0.7\linewidth]{figures/HyQ_roms}
  \caption{
           Reachable workspace and torso bounding box of HyQ. Each green shape represent a reachable workspace $W^k$ of a limb. The red shape is $W^0$.}
		   \label{fig:HyQ_roms}
\end{figure*}
Figure~\ref{fig:framework} illustrates our work flow.
\Pa and \Pb are addressed sequentially: From a given problem (a) we first plan a root guide path (b), before
extending it into a sequence of static equilibrium configurations (c). In the case where step (c) fails,
our framework invalidates the computed guide path, and restarts the planning from (b).

@@

%~ Finally, we define $dist(\mathbf{x}, O)$ as the minimal distance between a point $\mathbf{x}$ and the closest surface of the environment.

@@

\medskip
\textbf{The environment} $O$ is defined as the union of the obstacles $O_i$ that it contains. $O$ is represented
as a polygon soup (or mesh), where the normal of each surface is known. No further requirement is needed
by our approach. In this work, we assume the environment is fully known. State uncertainty is out of the scope of the paper.

@@

### 2017-10-04 body/rbprm.tex
finished pdf
rescaled figures 3 and 4

Given a start and a goal configurations, we aim at computing a guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow$ $\mathbb{R}^r$ verifying:
\begin{equation*} \label{eq:path}
\forall t \in [0,1], \mathbf{q}^0(t)  \in C_{Equil}^0
\end{equation*}
This means that any root configuration must be extended into a whole-body, static equilibrium configuration.
$C_{Equil}^0$  cannot be described analytically.

@@

\textbf{necessary conditions:}
For a contact to be possible, an obstacle $O_i \subset O$ necessarily intersects the reachable workspace $W(\mathbf{q}^{0})$ of the robot (Figure~\ref{fig:contact_gen}--1). Also the torso of the robot $W^0(\mathbf{q}^{0})$ must necessarily be collision-free.
Therefore we can define an outer approximation  $ \mathcal{C}^0_{\textrm{\it Nec}} \supset$ $C_{Contact}^0$ as: 
\begin{equation}
\mathcal{C}^0_{\textrm{\it Nec}} = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \textrm{ \textbf{and}}\ W^0(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \text{ and } & A_{torso}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%~ The inclusion $C_{Contact}^0$ $\subset \mathcal{C}^0_{\textrm{\it Nec}}$ is straightforward, but it is very important.
%~ Planning in $\mathcal{C}^0_{\textrm{\it Nec}}$ allows a strong reduction of the search space, while not discarding 
%~ any root configuration that could lead to a solution.

>>>>

Given start and goal configurations, we aim at computing a guide path $\mathbf{q}^0(t) : [0,1] \longrightarrow$ $\mathbb{R}^r$ verifying:
\begin{equation*} \label{eq:path}
\forall t \in [0,1], \mathbf{q}^0(t)  \in C_{Equil}^0
\end{equation*}
This means that any root configuration must be extended into a whole-body, static equilibrium configuration.
$C_{Equil}^0$  cannot be described analytically.

@@

\textbf{necessary conditions:}
For a contact to be possible, an obstacle $O_i \subset O$ necessarily intersects the reachable workspace $W(\mathbf{q}^{0})$ of the robot. % (Figure~\ref{fig:contact_gen}--a).
 Also the torso of the robot $W^0(\mathbf{q}^{0})$ must necessarily be collision-free.
Therefore we can define an outer approximation  $ \mathcal{C}^0_{\textrm{\it Nec}} \supset$ $C_{Contact}^0$ as: 
\begin{equation}
\mathcal{C}^0_{\textrm{\it Nec}} = \{ \mathbf{q}^0 : W(\mathbf{q}^{0}) \cap O \neq \emptyset \textrm{ \textbf{and}}\ W^0(\mathbf{q}^{0}) \cap O = \emptyset \} % \\ }
 %~ & \text{ and } & A_{torso}(\mathbf{q}^{root}) \cap W = \emptyset \}
\end{equation}
%~ The inclusion $C_{Contact}^0$ $\subset \mathcal{C}^0_{\textrm{\it Nec}}$ is straightforward, but it is very important.
%~ Planning in $\mathcal{C}^0_{\textrm{\it Nec}}$ allows a strong reduction of the search space, while not discarding 
%~ any root configuration that could lead to a solution.
